Statistical paradoxes in coronavirus case-counts: selection bias, measurement error, and the COVID-19 pandemic

### 2021-08-17 write-up/covid-writeup.tex
keeping general theory but going to clarify.  Then finalize paper!

Suppose there is a sequence of finite populations of size $N_{\nu}$ indexed by $\nu$.  Each finite population has an associated non-probability at time $t$ and probability samples of size $n$ at each time~$t=1,\ldots, T$.  Finally, let~$n_{FP}$ and $n_{FN}$ denote the sample sizes of $S_{FP}$ and $S_{FN}$ respectively.  For simplicity, dependency on $\nu$ is suppressed and the limiting process is represented by $N \to \infty$.

For each~$\nu$ and $t$, the estimates of $\eta = (\mu_t, \theta_t, FP, FN)$ are given by:
$$
\Phi (\eta) = \left (
\begin{array}{c}
\frac{1}{N} \sum_{j=1}^N I_{j,t} \frac{Y_{j,t} - FP - (1-FP-FN) \cdot \mu_t}{\pi_{j,t}} \\
\frac{1}{N \sum_{l=1}^L K_{t,t_l^\prime}} \sum_{l=1}^L K_{t,t_l^\prime} \left[ \sum_{j=1}^N I_{j,t^\prime} X_{j,t^\prime_l} - \frac{1}{N} \sum_{j = 1}^N \tilde I_{j,t_l^\prime} \tilde W_{j,t_l^\prime}  \pi_{j,t_l^\prime} X_{j,t_l^\prime} \right] \\
\frac{1}{n_{FP}} \sum_{j \in S_{FP}} \frac{Z_j}{FP} - \frac{1-Z_j}{1-FP} \\
\frac{1}{n_{FN}} \sum_{j \in S_{FN}} \frac{\tilde Z_j}{FN} - \frac{1-\tilde Z_j}{1-FN} \\
\end{array}
\right ) = {\bf 0}
$$
where $\pi_{j,t^\prime} = \pi (X_{j,t^\prime}; \theta_t)$, $Z_j$ is an indicator of a false positive in the sample $S_{FP}$  and $\tilde Z_j$ is an indicator of a false negative in the sample $S_{FN}$.  We assume the synthetic $|S_{FP}|^{-1} \sum_{j \in S_{FP}} Z_j = 0.024$ and $|S_{FP}|^{-1} \sum_{j \in S_{FP}} Z_j = 0.30$.  \textcolor{red}{Sample sizes, denoted $n_{FP}$ and $n_{FN}$ respectively, are chosen to achieve desired estimator variance, i.e., $\frac{0.024 \cdot (0.976)}{n_{FP}} = \sigma^2_{FP}$ and $\frac{0.30 \cdot 0.70}{n_{FN}} = \sigma^2_{FN}$.}

>>>>

uppose there is a sequence of finite populations of size $N_{\nu}$ indexed by $\nu$.  Each finite population has an associated non-probability at time $t$ of  size~$\tilde n$ and $L_\nu$ probability samples of fixed size $n$ drawn at equally spaced times $\{ t^\prime_l \}_{l=1}^L$ over the study window~$[0,T]$. Let~$\Delta_\nu$ denote the gap times between consecutive sample times. Finally, let~$n_{FP}$ and $n_{FN}$ denote the sample sizes of $S_{FP}$ and $S_{FN}$ respectively.  For simplicity, dependency on $\nu$ is suppressed and the limiting process is represented by $N \to \infty$.

For each~$\nu$ and $t$, the estimates of $\eta = (\mu_t, \theta_t, FP, FN)$ are given by:
$$
\Phi (\eta) = \left (
\begin{array}{c}
\frac{1}{N} \sum_{j=1}^N I_{j,t} \frac{Y_{j,t} - FP - (1-FP-FN) \cdot \mu_t}{\pi_{j,t}} \\
\frac{1}{N \sum_{l=1}^L K_{t,t_l^\prime}} \sum_{l=1}^L K_{t,t_l^\prime} \left[ \sum_{j=1}^N I_{j,t^\prime} X_{j,t^\prime_l} - \frac{1}{N} \sum_{j = 1}^N \tilde I_{j,t_l^\prime} \tilde W_{j,t_l^\prime}  \pi_{j,t_l^\prime} X_{j,t_l^\prime} \right] \\
\frac{1}{n_{FP}} \sum_{j \in S_{FP}} \frac{Z_j}{FP} - \frac{1-Z_j}{1-FP} \\
\frac{1}{n_{FN}} \sum_{j \in S_{FN}} \frac{\tilde Z_j}{FN} - \frac{1-\tilde Z_j}{1-FN} \\
\end{array}
\right ) = {\bf 0}
$$
where $\pi_{j,t^\prime} = \pi (X_{j,t^\prime}; \theta_t)$, $Z_j$ is an indicator of a false positive in the sample $S_{FP}$  and $\tilde Z_j$ is an indicator of a false negative in the sample $S_{FN}$.  We assume the $|S_{FP}|^{-1} \sum_{j \in S_{FP}} Z_j = 0.024$ and $|S_{FP}|^{-1} \sum_{j \in S_{FP}} Z_j = 0.30$.  Sample sizes, denoted $n_{FP}$ and $n_{FN}$ respectively, are chosen to achieve desired estimator variance, i.e., $\frac{0.024 \cdot (0.976)}{n_{FP}} = \sigma^2_{FP}$ and $\frac{0.13 \cdot 0.87}{n_{FN}} = \sigma^2_{FN}$. Here we set $\sigma^2_{FP} = 0.02^2$ and $\sigma_{FN}^2 = 0.05^2$ which yield $n_{FP} \approx 59$ and $n_{FN} \approx 45$ respectively.
